R Notebook

### 2017-02-23 manuscript/draft.Rmd
Draft of Title
Add possible changes in model performance w/lead time

# Title

@@

In general the accuracy of forecasts decreases with the length of time into the
future being forecast [@petch2015]. This decay in accuracy and associated
forecast horizons should be considered when evaluating forecasts and comparing
models.

>>>>

# Moving towards large-scale data-intensive forecasting of species richness in breeding birds

@@

In general the accuracy of forecasts decreases with the length of time into the
future being forecast [@petch2015]. This decay in accuracy and the potential for
different rates of decay to result in different relative model performance at
different lead times should be considered when evaluating forecasts and
comparing models.
